Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-31 nir_companions.tex
More corrections

% Abstract of the paper
\begin{abstract}
    {\rd A}We perform an exploratory study on how to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to measure or constrain their masses, thereby asserting their stellar nature or discarding it. {\rd B}We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations with a synthetic binary model comprised of two PHOENIX-ACES spectra, representing the spectra from the host and companion. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models.
    {\rd C}The direct subtraction method failed to detect the signature of the companions. The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery performs on simulated observations and discuss reasons for the non-detection observed. {\rd From the injection-recovery analysis this technique in, its current form, is insufficient below 3800~K which corresponds to an upper mass limit for the companions to be around \(\rm 600^{+20}_{-40}~M_{Jup}\)}. {\rd D}This work highlights the challenges in the spectral detection of faint BD companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and attempt companion recovery at low companion/host flux ratios below 3\%, finding a high upper mass limit from the technique. {\rd This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.}
\end{abstract}

@@

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

@@

Spectral observations of binary systems contain the spectra of both bodies, in proportion to their flux ratio, and Doppler shifted relative to each other due to their orbital motion. One technique to recover the spectra of the companion is secondary reconstruction through a differential spectrum~\citep{ferluga_separating_1997}. Spectra from different phases are shifted to the host stars rest frame and subtracted to mutually cancel out the spectrum of the host star allowing the faint companion spectra to become visible. Advances in high-resolution and near-infrared capabilities should enable this technique to be applied to BDs and planet companions, in which smaller RV shifts can be resolved and the contrast ratio of the smaller companion is improved.

Observing in the near-infrared is specifically desirable for the cooler sub-stellar and giant planet companions as their thermal emission is stronger in the infrared compared to the optical. This improves the contrast ratio between the host star and companion, providing favorable conditions for their detection and spectral separation. CRIRES, a high resolution near-infrared spectrograph, has made many prominent advances in recent years with the detection of atmospheric constituents, such as \(\textrm{CO} \) and \(\textrm{H}_{2}\textrm{O} \), atmospheric winds and thermal profiles, rotation and orbital motion, for both transiting and non-transiting planets~\citep[e.g.][]{snellen_orbital_2010, brogi_signature_2012, rodler_weighing_2012, dekok_detection_2013, brogi_carbon_2014, snellen_fast_2014, piskorz_evidence_2016, brogi_rotation_2016}.

The higher temperature and relatively larger size of BDs compared to giant-planets makes the development of spectral recovery techniques for BD companions a logical step towards the spectroscopic detection of planetary atmospheres. There has been the recent installation and continued development of many new high-resolution near-InfraRed (nIR) spectrographs, such as, CARMENES~\citep{quirrenbach_carmenes_2014}, NIRPS~\citep{bouchy_nearinfrared_2017} or SPIRou~\citep{artigau_spirou_2014}, as well as, the CRIRES+~\citep{dorn_crires_2016} upgrade. These new instruments motivate the study of nIR-oriented methodologies for spectral recovery, and are of high importance due to the larger planet-to star flux ratio in the near-IR than in the visible.

@@

\textit{K}-band spectra were obtained with the goal to achieve a direct detection of the companion spectra through the application of a spectral-differential approach. Doing so would enable a further constraint to be placed on their masses. The \textit{K}-band is used to achieve a high contrast relative to the host star, detected in the extreme V-K color indexes (>7.8).

@@

The observations were performed in service mode during period 89 with run ID.~089.C-0977(A) between April and August 2012. An observation is composed of 8 individual spectra each with an integration time of 180 seconds, observed in the ABBAABBA nod cycle pattern to obtain a high (>180) signal-to-noise when combined.

@@

and \(A \), \(\mu \), \(\sigma \) are the amplitude, central wavelength, and standard deviation for each line respectively. {\rd Although telluric lines are actually Voigt profiles, they are not fully resolved in the near-infrared and their shape is dominated by the instrumental profile. The instrumental profile for CRIRES  has been shown to be well represented by a Gaussian \citep{seifahrt_synthesising_2010a}, at-least below a SNR\(\sim300\).}

@@

The PHOENIX-ACES models include dust in equilibrium with the gas phase while ignoring dust opacity and does not include any mixing/settling which is important for cooler BD atmospheres. They set a minimum library \(T_{\textrm{eff}} = 2300\)~K to avoid the temperatures at which the modeling of clouds is necessary. This unfortunately limits the use of this library for this technique to the largest mass companions in our sample. For example a \(T_{\textrm{eff}}=2300\)~K corresponds to a BD with (\(\rm M\sim84~M_{Jup}\) at 5 Gyr from the~\citet{baraffe_evolutionary_2003} evolutionary models.

There are other models that extend below 2300~K such as the BT-Settl models\citep{allard_btsettl_2013,baraffe_new_2015}. These are discussed in Sect.~\ref{subsubsec:bt-settl}.

@@

In this work we use the effective radius (PHXREFF keyword) of each component from the PHOENIX model headers. This is the radius used in modeling of the stellar atmospheres. We use this radii as it is directly tied to each model spectrum, and already available. The ratio of the radii from the two synthetic spectra in the binary models are provided in Table~\ref{tab:example_params}.

@@

The targets analyzed here do not have transits, but if the radius ratio can be independently determined from the photometric transit method~\citep{deeg_photometric_1998} then this could be used to constrain the radius ratio used when combing the binary model spectra instead.

@@

\subsection{Reducing parameters}
\label{subsec:reduce-params}
The high dimensionality of the binary model makes it computationally challenging and difficult to analyze the \(\chi^2\) space. 
For reference, the multiplicative parameter space is squared when increasing from one spectral component in the single model to a binary model, and therefore becomes computationally expensive. In general the number of possible parameter combinations for \(c\) spectral components each with a grid of \(m\) models increases to \(c^m\). If the full set of PHOENIX-ACES library spectra (66456) is explored with a binary fit then this naively balloons to over 4.4 billion possible combinations. Half of these are not unique as the host and companion components are swapped. This is the worst case scenario and we implement a number of assumptions to vastly reduce the parameter-space enabling faster computation.

@@

The large numbers stated above also do not include the RV grid for each component. The RV grid is user defined and the number of spectra /models to consider increases when the RV grid step size is decreased (finer RV resolution). We can reduce the RV grid space significantly by tailoring it to the target being examined. For each target, we use the estimated RV values from the observation time and orbital parameters, given in Table~\ref{tab:observations} as a center starting point for the \({rv}_1\) and \({rv}_2\) values and increment the RV within a few FWHM around those values, or out to the targets \(\rm K_1\) and estimated \(\rm K_2\) values.

@@

The results of two example binary simulations are displayed in Figs.~\ref{fig:Mdwarf_contours} and ~\ref{fig:HD211847_simulated_contours}, both simulated with a SNR of 150. The input and recovered parameters for the binary components are indicated by the red circles and yellow stars respectively, and are given in Table~\ref{tab:example_params}. 
The 3-\(\sigma\) contour is shown in white on the plots to indicate the shape of the confidence level only. The 1-\(\sigma\) contours are not shown here as they are much smaller than the temperature grid step and are not easy to visualize at this scale as they are often smaller than the marker shown at the minimum location. Each colored rectangle is centered on the grid point, with its shape indicating the resolution of the grid space searched.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.8\hsize]{images/HD211847_example_pcolors.pdf}
    \caption{Similar to Fig.~\ref{fig:Mdwarf_contours}, \(\chi^2\) results for companion recovery of a simulated binary observation similar to {HD 211847}, (\(T_{\textrm{eff}_1} = 5800\)~K, \(T_{\textrm{eff}_2}=3200\)~K). The top right plot shows the application of a single component model (\(C^1\)) while the other three are using a binary model (\(C^2\)). Both left hand panels show the distribution of host temperature and host RV. The top right panel shows the distribution for host and companion temperature, and the bottom right the companion temperature and radial velocity.
        The red circle and yellow star indicate the location of the simulation input and recovered parameters respectively.
        The white line shows a 3-\(\sigma\) confidence level about the minimum \(\chi^2\) solution grid point. Each box is centered on the parameter values and shows the grid resolution.}
    \label{fig:HD211847_simulated_contours}
\end{figure*}

@@

The \(\chi^2_{red}\) values for the single and binary models are 21 and 19 respectively, which indicates that both models are a poor fit to the observations. We plot the binary model for the best fit solution alongside the observed spectra in Fig.~\ref{fig:visualinspection-hd2118471}. We see that there is a large spectral mismatch between the synthetic models and the observation. Extra wavelength masking was applied to many of the largest mismatched synthetic lines to remove their influence. The grey areas mark regions which have been masked out, either from the centers of deep telluric lines (the thin masks matching spectral gaps), or the more prominent mismatched lines in the synthetic spectrum excluded from the \(\chi^2\) analysis. One clear example of a mismatched line is a synthetic line at 2132.5~nm that is clearly not observed in detector 2 (top right). Even with the majority of the mismatched lines removed the detection of the companion was still unsuccessful.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.9\linewidth]{images/visualize_result_residuals.pdf}
    \caption{Comparison between the observed {HD 211847} spectrum (blue) and the best fit synthetic binary model (orange dashed) for each detector. The bottom section of each panel shows the residuals between the parts of the observation used in the \(\chi^2\) fit and recovered binary model (\(\rm O-C^2\)) in purple. The red dashed line shows the difference between the recovered binary model and the binary model with the exact same parameters except for the estimated companion temperature of 3200~K (\(\rm C^2[3200K]- C^2\)). The grey shading indicated the wavelength regions where masking has been applied. The thinner masked regions that match with cuts in the observed spectra are where the centers of deep (>5\%) telluric lines that have been masked out are.}
    \label{fig:visualinspection-hd2118471}
\end{figure*}

@@

For {HD 30501} the injection onto synthetic and observed spectra produce similar results. At temperatures above 3800~K in both the real and synthetic the injected companion is recovered within 100~K. For injected companion temperatures below 3800~K the temperature recovered is systematically higher than the injected value. This indicates that the companion is not correctly recovered and is affected by the added noise. We determine this temperature to be the upper temperature limit for the recovery. For the other stars we could not conclude on the upper limit due to spectral mismatch issues. In these cases we use the results from the synthetic injection to derive a temperature recovery cutoff for each target, each simulated with the closest host star spectrum.

@@

\begin{figure}
    \centering
    \includegraphics[width=\hsize]{images/chi2_shape_investigation_sigmas.pdf}
    \caption{(top) Companion temperature verses \(\chi^2\) for simulations with different injected companion temperatures. Other fixed parameters for these fully synthetic simulations was \(T_{\textrm{eff}_1}=5200\)~K, \(\textrm{logg}_1=4.5\), \(\textrm{logg}_2=5.0\), and both [Fe/H] = 0.0. A fixed Gaussian noise corresponding to a SNR of 300 was used.
        (bottom) A close up view of \(\chi^2\) < 15. The three horizontal grey lines indicate the 1, 2, 3 sigma with 2 degrees of freedom. The vertical dotted lines indicate the location of the minimum \(\chi^2\) recovered for each companion. The black solid vertical in both panels shows the 2300~K cutoff of the PHOENIX-ACES models}
    \label{fig:injection_shape}
\end{figure}

@@

Using the temperature cutoff values, we derive an upper mass limit for the companions around our stars using the~\cite{baraffe_new_2015} evolutionary models, finding the closest point matching the spectral temperature cutoff and \(\rm logg=5.0\). These values are given in Table~\ref{tab:mass_limits} and are between 560 and 618 \(\rm M_{jup}\). The flux ratio between the cutoff and the host star are also provided for, being between 5 and 15\% in this wavelength span.

\section{Discussion}
\label{sec:discussion}
The spectral differential and the synthetic recovery methods attempted here were both unsuccessful in a detection of the BD companion spectra.  The upper mass limits of \(600^{+20}_{-40} \) we set for these companions is very high, roughly six times higher then the BD mass limit \(\rm\sim 80-90~M_{Jup}\).
We discuss potential reasons and solutions for these poor results below, list the lessons learned in this exploratory study, and provide some guidance for any future attempts with these methods. {\rd We do note that there have been recent works, that have had successful detection of non-transiting giant planets, they use a different technique cross correlation and maximum likelyhood....} They are successful due to spectra with much higher SNR, longer wavelength range.    XXXXXXXXXXXXXXXXXXXXXXX

\subsection{Synthetic recovery limitations}
\label{subsec:limitations}
In this section we discuss some of the limitations from this synthetic recovery method and some options to overcome some of these.

\subsubsection{Mismatch in synthetic models}
\label{subsubsec:mismatch}
We believe the mismatch between the observation and synthetic spectra is the main cause of the unsuccessful companion detection, impacting the recovery in two ways. The mismatch causes the \(\chi^2\) values to be large in general, but also causes the companion temperature to be pushed to higher temperatures.

In our examples the logg and metallicity of the synthetic models are held fixed, leaving only temperature to vary. The temperature impacts the synthetic spectral models in two main ways: the flux level of the continuum; and the number and strength of the absorption lines. In the binary model the contributions from the individual components is scaled by the flux ratio. If the temperature of the companion increases then the flux and radius of the companion increases. Its contribution of the companion to the binary model increases and the flux ratio \(\rm F_1/F_2\) decreases. This effectively makes the lines of the spectrum of the host component relatively smaller in the normalized binary model spectrum. Due to the initial mismatch of synthetic spectral lines, a decrease in relative strength of the host lines decreases the \(\chi^2\) value, and is a better ``match'' to the observation. This causes the recovered temperature of the companion to be higher than expected, >2000~K higher if allowed by the exploration grid. The \(\chi^2\) approach is dominated by reducing the mismatch in the spectrum of the host rather than detecting the spectra of the companion.
This spectral mismatch is not observed in the simulations in Sect.~\ref{subsec:simulated_binaries} since they are created using the synthetic spectra themselves, and hence they do recover the correct host spectra.

@@

In Table~\ref{tab:line_contributions} we calculate some properties of the spectral lines in the PHOENIX-ACES library between 2110--2160~nm. We count the number of spectral lines (\emph{no.\ lineses}) deeper than 5\%, and take the average depth (\emph{avg.\ depth}) of these lines. The contribution \emph{cont.\ depth} of the companion lines to a combined spectrum accounts for the flux ratio between the two components. Here we use a Sun-like host with \(T_{\textrm{eff}_1}=5800\)~K. This simplified combination neglects the continuum shapes of both spectral components and uses the average flux ratios for this wavelength range. The PHOENIX-ACES spectra in the temperature range of 2500--5000~K shown in Fig.~\ref{fig:comp_spectra} can be used to get a visual indication of the line density and depth measured here.

@@

The bump observed at 5100~K in the \(\chi^2\) curves is due to a discontinuity in the PHOENIX-ACES modeling. The ``reference wavelength defining the mean optical depth grid'' is changed at 5000~K~\citep[][Sect. 2.3]{husser_new_2013}. Care needs to be taken if trying to detect a companion near this temperature.

@@

\subsubsection{Component RV separation}
\label{subsubsec:rv_seperation}
Another factor which could contribute to an unsuccessful detection is the RV separation between the host and companion, \(rv_2\). Estimates for our observations are given in the last column of Table~\ref{tab:observations}. If \({rv}_2\) is small compared to the line width, then all the same lines of both components will be blended. This is indeed the case for {HD 4747}, {HD 211847}, and {HD 202206} with expected \(|{rv}_2| < 2\)\kmps{}. This may have contributed to the lack of recovery with both components of the binary model trying to fit to the same features. This may even cause some correlation between the parameters of the two components. The RV separation of the two components changes with orbital phase. Having multiple spectra of the same target distributed in phase may allow the RV of the spectral components to be better recovered~\citep[e.g.][]{czekala_disentangling_2017, sablowski_spectral_2016}.

\subsubsection {Wavelength range}
\label{subsubsec:wavelenght_range_limitation}
The wavelength choice for the spectra analyzed here, observed with the intention to apply the spectral differential technique, was selected due to the location of the \textit{K}-band telluric absorption window. This wavelength range, with a narrow wavelength range \(\sim50\)~nm set by the CRIRES instrument. This wavelength range is likely not the best choice for the proposed study.

Changing the wavelength coverage to regions with lines sensitive to stellar parameters for both stars and BDs, as well as using a larger wavelength range that will be achieved by CRIRES+, may help to improve the recovery results of the companion recovery technique presented here. We note that if the wavelength range is increased by taking separate observations at different wavelengths, not covered by a single exposure, then changes in the RV of both components between the different wavelength observations may need to be accounted for.

\subsubsection{The BT-Settl models}
\label{subsubsec:bt-settl}
We note that the PHOENIX-ACES models are not the only spectral libraries available with the other notable library considered for this work is the BT-Settl models, ~\citep{allard_model_2010,allard_btsettl_2013,baraffe_new_2015}. The included modeling of dust and cloud formation, as well as hydro-dynamical modeling atmospheric mixing/settling for atmospheres with \(T_{\textrm{eff}}\) below \(\sim2600\)~K, make the BT-Settl models valid across the regime from stars to BDs as cool as 400~K. As the BT-Settl models are suitable to model the atmospheres of the brown dwarfs they would be useful for the companion recovery technique developed here. However, as shown in Sect.~\ref{subsection:results-hd211847} and~\ref{subsection:injection-recovery}, we were unable to successfully recover the 155 \(\rm M_J\) (\(T_{\textrm{eff}}\sim3200\)~K) low mass star companion of {HD 211847} and derived a temperature upper limit for our methodology of around 3800~K. These are both well above the 2300~K cutoff of the PHOENIX-ACES models and for the onset of dust- and cloud-formation phenomena, at 2600 K..

>>>>

% Abstract of the paper
\begin{abstract}
   {\rd In this paper we attempt to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to assert or discard their stellar nature. We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations of a synthetic binary model comprised of two PHOENIX-ACES spectra. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models. The direct subtraction method failed to detect the signature of the companions due to poor observational constraints. The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery fitting performs on simulated observations and discuss reasons for the non-detection observed. {\rd From the injection-recovery analysis, this technique in its current form, is insufficient to recover a companion below 3800~K which corresponds to an upper mass limit for the companions around \(\rm 600~M_{Jup}\)}. This work highlights the challenges in the spectral detection of faint companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and companion detection with synthetic models at low companion/host flux ratios below 3\%.}
\end{abstract}

@@

@@

Spectral observations of binary systems contain the spectra of both bodies, in proportion to their flux ratio, and Doppler shifted relative to each other due to their orbital motion. One technique to recover the spectra of the companion is secondary reconstruction through a differential spectrum~\citep{ferluga_separating_1997}. Spectra from different phases are shifted to the host stars rest frame and subtracted to mutually cancel out the spectrum of the host star allowing the faint companion spectra to become visible. Advances in high-resolution and near-infrared capabilities should enable this technique to be applied to BDs and planet companions, in which smaller RV shifts can be resolved and the contrast ratio of the smaller companion is improved. {\rd Identify and separating spectral components is  MENTION  KOBL, mehtods for detecting secondaries.}

Observing in the near-infrared is specifically desirable for the cooler sub-stellar and giant planet companions as their thermal emission is stronger in the infrared compared to the optical. This improves the contrast ratio between the host star and companion, providing favourable conditions for their detection and spectral separation. CRIRES, a high resolution near-infrared spectrograph, has made many prominent advances in recent years with the detection of atmospheric constituents, such as \(\textrm{CO} \) and \(\textrm{H}_{2}\textrm{O} \), atmospheric winds and thermal profiles, rotation and orbital motion, for both transiting and non-transiting planets~\citep[e.g.][]{snellen_orbital_2010, brogi_signature_2012, rodler_weighing_2012, dekok_detection_2013, brogi_carbon_2014, snellen_fast_2014, piskorz_evidence_2016, brogi_rotation_2016}.

The higher temperature and relatively larger size of BDs compared to giant-planets makes the development of spectral recovery techniques for BD companions a logical step towards the spectroscopic detection of planetary atmospheres. There has been the recent installation and continued development of many new high-resolution near-InfraRed (nIR) spectrographs, such as, {CARMENES}~\citep{quirrenbach_carmenes_2014}, NIRPS~\citep{bouchy_nearinfrared_2017} or SPIRou~\citep{artigau_spirou_2014}, as well as, the CRIRES+~\citep{dorn_crires_2016} upgrade. These new instruments motivate the study of nIR-oriented methodologies for spectral recovery, and are of high importance due to the larger planet-to-star flux ratio provided by near-IR compared to the visible.

@@

\textit{K}-band spectra were obtained with the goal to achieve a direct detection of the companion spectra through the application of a spectral-differential approach. Doing so would enable a further constraint to be placed on their masses. The \textit{K}-band is used to achieve a high contrast relative to the host star, detected in the extreme V-K colour indexes (>7.8).

@@

The observations were performed in service mode during period 89 with run ID.~089.C-0977(A) between April and August 2012. An observation is composed of 8 individual spectra each with an integration time of 180 seconds, observed in a ABBAABBA nod cycle pattern to obtain a high (>180) signal-to-noise when combined.

@@

and \(A \), \(\mu \), \(\sigma \) are the amplitude, central wavelength, and standard deviation for each line respectively. {\rd Although telluric lines are actually Voigt profiles, they are not fully resolved in the near-infrared and their shape is dominated by the instrumental profile. The instrumental profile for CRIRES  has been shown to be well represented by a Gaussian \citep{seifahrt_synthesising_2010}.}

@@

The PHOENIX-ACES models include dust in equilibrium with the gas phase while ignoring dust opacity and does not include any mixing/settling which is important for cooler BD atmospheres. They set a minimum library \(T_{\textrm{eff}} = 2300\)~K to avoid the temperatures at which the modelling of clouds is necessary. This unfortunately limits the use of this library for this technique to the largest mass companions in our sample. For example a \(T_{\textrm{eff}}=2300\)~K corresponds to a BD with (\(\rm M\sim84~M_{Jup}\) at 5 Gyr from the~\citet{baraffe_evolutionary_2003} evolutionary models.

There are other models that extend below 2300~K such as the {BT-Settl} models\citep{allard_btsettl_2013,baraffe_new_2015}. These are discussed in Sect.~\ref{subsubsec:BT-Settl}.

@@

In this work we use the effective radius (PHXREFF keyword) of each component from the PHOENIX model headers. This is the radius used in modelling of the stellar atmospheres. We use this radii as it is directly tied to each model spectrum, and already available. The ratio of the radii from the two synthetic spectra in the binary models are provided in Table~\ref{tab:example_params}.

@@

The targets analysed here do not have transits, but if the radius ratio can be independently determined from the photometric transit method~\citep{deeg_photometric_1998} then this could be used to constrain the radius ratio used when combing the binary model spectra instead.

@@

\subsection{Reducing parameters}
\label{subsec:reduce-params}
The high dimensionality of the binary model makes it computationally challenging and difficult to analyse the \(\chi^2\) space. 
For reference, the multiplicative parameter space is squared when increasing from one spectral component in the single model to a binary model, and therefore becomes computationally expensive. In general the number of possible parameter combinations for \(c\) spectral components each with a grid of \(m\) models increases to \(c^m\). If the full set of PHOENIX-ACES library spectra (66456) is explored with a binary fit then this naively balloons to over 4.4 billion possible combinations. Half of these are not unique as the host and companion components are swapped. This is the worst case scenario and we implement a number of assumptions to vastly reduce the parameter-space enabling faster computation.

@@

The large numbers stated above also do not include the RV grid for each component. The RV grid is user defined and the number of spectra /models to consider increases when the RV grid step size is decreased (finer RV resolution). We can reduce the RV grid space significantly by tailoring it to the target being examined. For each target, we use the estimated RV values from the observation time and orbital parameters, given in Table~\ref{tab:observations} as a centre starting point for the \({rv}_1\) and \({rv}_2\) values and increment the RV within a few FWHM around those values, or out to the targets \(\rm K_1\) and estimated \(\rm K_2\) values.

@@

The results of two example binary simulations are displayed in Figs.~\ref{fig:Mdwarf_contours} and ~\ref{fig:HD211847_simulated_contours}, both simulated with a SNR of 150. The input and recovered parameters for the binary components are indicated by the red circles and yellow stars respectively, and are given in Table~\ref{tab:example_params}. 
The 3-\(\sigma\) contour is shown in white on the plots to indicate the shape of the confidence level only. The 1-\(\sigma\) contours are not shown here as they are much smaller than the temperature grid step and are not easy to visualize at this scale as they are often smaller than the marker shown at the minimum location. Each coloured rectangle is centred on the grid point, with its shape indicating the resolution of the grid space searched.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.8\hsize]{images/HD211847_example_pcolors.pdf}
    \caption{Similar to Fig.~\ref{fig:Mdwarf_contours}, \(\chi^2\) results for companion recovery of a simulated binary observation similar to {HD 211847}, (\(T_{\textrm{eff}_1} = 5800\)~K, \(T_{\textrm{eff}_2}=3200\)~K). The top right plot shows the application of a single component model (\(C^1\)) while the other three are using a binary model (\(C^2\)). Both left hand panels show the distribution of host temperature and host RV. The top right panel shows the distribution for host and companion temperature, and the bottom right the companion temperature and radial velocity.
        The red circle and yellow star indicate the location of the simulation input and recovered parameters respectively.
        The white line shows a 3-\(\sigma\) confidence level about the minimum \(\chi^2\) solution grid point. Each box is centred on the parameter values and shows the grid resolution.}
    \label{fig:HD211847_simulated_contours}
\end{figure*}

@@

The \(\chi^2_{red}\) values for the single and binary models are 21 and 19 respectively, which indicates that both models are a poor fit to the observations. We plot the binary model for the best fit solution alongside the observed spectra in Fig.~\ref{fig:visualinspection-hd2118471}. We see that there is a large spectral mismatch between the synthetic models and the observation. Extra wavelength masking was applied to many of the largest mismatched synthetic lines to remove their influence. The grey areas mark regions which have been masked out, either from the centres of deep telluric lines (the thin masks matching spectral gaps), or the more prominent mismatched lines in the synthetic spectrum excluded from the \(\chi^2\) analysis. One clear example of a mismatched line is a synthetic line at 2132.5~nm that is clearly not observed in detector 2 (top right). Even with the majority of the mismatched lines removed the detection of the companion was still unsuccessful.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.8\linewidth]{images/visualize_result_residuals.pdf}
    \caption{Comparison between the observed {HD 211847} spectrum (blue) and the best fit synthetic binary model (orange dashed) for each detector. The bottom section of each panel shows the residuals between the parts of the observation used in the \(\chi^2\) fit and recovered binary model (\(\rm O-C^2\)) in purple. The red dashed line shows the difference between the recovered binary model and the binary model with the exact same parameters except for the estimated companion temperature of 3200~K (\(\rm C^2[3200K]- C^2\)). The grey shading indicated the wavelength regions where masking has been applied. The thinner masked regions that match with cuts in the observed spectra are where the centres of deep (>5\%) telluric lines that have been masked out are.}
    \label{fig:visualinspection-hd2118471}
\end{figure*}

@@

For {HD 30501} the injection onto synthetic and observed spectra produce similar results. At temperatures above 3800~K in both the real and synthetic the injected companion is recovered within 100~K. For injected companion temperatures below 3800~K the temperature recovered is systematically higher than the injected value. This indicates that the companion is not correctly recovered and is affected by the added noise. We determine this temperature to be the upper temperature limit for the recovery. For the other stars we could not conclude on the upper limit due to spectral mismatch issues. In these cases we use the results from the synthetic injection to derive a temperature recovery cut-off for each target, each simulated with the closest host star spectrum.

@@

\begin{figure}
    \centering
    \includegraphics[width=\hsize]{images/chi2_shape_investigation_sigmas.pdf}
    \caption{(top) Companion temperature verses \(\chi^2\) for simulations with different injected companion temperatures. Other fixed parameters for these fully synthetic simulations was \(T_{\textrm{eff}_1}=5200\)~K, \(\textrm{logg}_1=4.5\), \(\textrm{logg}_2=5.0\), and both [Fe/H] = 0.0. A fixed Gaussian noise corresponding to a SNR of 300 was used.
        (bottom) A close up view of \(\chi^2\) < 15. The three horizontal grey lines indicate the 1, 2, 3 sigma with 2 degrees of freedom. The vertical dotted lines indicate the location of the minimum \(\chi^2\) recovered for each companion. The black solid vertical in both panels shows the 2300~K cut-off of the PHOENIX-ACES models}
    \label{fig:injection_shape}
\end{figure}

@@

Using the temperature cut-off values, we derive an upper mass limit for the companions around our stars using the~\cite{baraffe_new_2015} evolutionary models, finding the closest point matching the spectral temperature cut-off and \(\rm logg=5.0\). These values are given in Table~\ref{tab:mass_limits} and are between 560 and 618 \(\rm M_{Jup}\). The flux ratio between the cut-off and the host star are also provided for, being between 5 and 15\% in this wavelength span.

\section{Discussion}
\label{sec:discussion}
The spectral differential and the synthetic recovery methods attempted here were both unsuccessful in a detection of the BD companion spectra.  The upper mass limits of \(600^{+20}_{-40} \) we set for these companions is very high, roughly six times higher then the BD mass limit \(\rm\sim 80-90~M_{Jup}\).
We discuss potential reasons and solutions for these poor results below, list the lessons learned in this exploratory study {\rd of this dataset}, and provide some guidance for any future attempts with these methods.

\subsection{Synthetic recovery limitations}
\label{subsec:limitations}
In this section we discuss some of the limitations from this synthetic binary method and some options to overcome some of these.

\subsubsection{Mismatch in synthetic models}
\label{subsubsec:mismatch}
We believe the spectral mismatch between the observation and synthetic spectra is the main cause of the unsuccessful companion detection with the $\chi^2$ method, impacting the recovery in two ways. The spectral mismatch causes the \(\chi^2\) values to be large in general, but also causes the companion temperature to be pushed to higher temperatures, to the constraints of the grid.

In our examples the logg and metallicity of the synthetic models are held fixed, leaving only temperature to vary. The temperature impacts the synthetic spectral models in two main ways: the flux level of the continuum; and the number and strength of the absorption lines. In the binary model the contributions from the individual components is scaled by the flux ratio. If the temperature of the companion increases then the flux and radius of the companion increases. The contribution of the companion to the binary model increases and the flux ratio \(\rm F_1/F_2\) decreases. This effectively makes the lines of the spectrum of the host component relatively smaller in the normalized binary model spectrum. Due to the large initial mismatch of synthetic spectral lines of the host, a decrease in relative strength of the host lines decreases the \(\chi^2\) value, and is a better ``match'' to the observation. This causes the recovered temperature of the companion to be much higher than expected. If the companion temperature grid is allowed to extend it will recover a companion with a temperature >2000~K above the expected temperature. The \(\chi^2\) approach is dominated by reducing the mismatch in the spectrum of the host rather than actually detecting the spectra of the companion. When preforming the simulations  in Sect.~\ref{subsec:simulated_binaries} there is no spectral mismatch between the simulation and the models, hence they do recover the correct host spectra and get closer values for the companion.

@@

In Table~\ref{tab:line_contributions} we calculate some properties of the spectral lines in the PHOENIX-ACES library between 2110--2160~nm. We count the number of spectral lines (\emph{no.\ lines}) deeper than 5\%, and take the average depth (\emph{avg.\ depth}) of these lines. The contribution \emph{cont.\ depth} of the companion lines to a combined spectrum accounts for the flux ratio between the two components. Here we use a Sun-like host with \(T_{\textrm{eff}_1}=5800\)~K. This simplified combination neglects the continuum shapes of both spectral components and uses the average flux ratios for this wavelength range. The PHOENIX-ACES spectra in the temperature range of 2500--5000~K shown in Fig.~\ref{fig:comp_spectra} can be used to get a visual indication of the line density and depth measured here.

@@

The bump observed at 5100~K in the \(\chi^2\) curves is due to a discontinuity in the PHOENIX-ACES modelling. The ``reference wavelength defining the mean optical depth grid'' is changed at 5000~K~\citep[][Sect. 2.3]{husser_new_2013}. Care needs to be taken if trying to detect a companion near this temperature.

@@

\subsubsection{Component RV separation}
\label{subsubsec:rv_seperation}
Another factor which could contribute to an unsuccessful detection is the RV separation between the host and companion, \(rv_2\). Estimates for our observations are given in the last column of Table~\ref{tab:observations}. If \({rv}_2\) is small compared to the line width, then all the same lines of both components will be blended. This is indeed the case for {HD 4747}, {HD 211847}, and {HD 202206} with expected \(|{rv}_2| < 2\)\kmps{}, {\rd due to poor observational planning}. This may have contributed to the lack of recovery with both components of the binary model attempting to fit the same features. This may even cause correlation between the parameters of the two components. The RV separation of the two components changes with orbital phase. Having multiple spectra of the same target distributed in phase may allow the RV of the spectral components to be better recovered~\citep[e.g.][]{czekala_disentangling_2017, sablowski_spectral_2016}.

\subsubsection {Wavelength range}
\label{subsubsec:wavelenght_range_limitation}
{\rd The wavelength range for these observations was chosen specifically due to the location of the \textit{K}-band telluric absorption window. This was to reduce telluric contamination present in the spectra intended for the spectral differential technique. The wavelength range is also very narrow (\(\sim50\)~nm) set by the CRIRES instrument. The small number and inconsistent distribution telluric lines made the wavelength calibration method using the telluric lines difficult in some regions (specifically detectors 2 and 3). For the $\chi^2$ fitting of faint companions this narrow wavelength region likely not the best given the small number of stellar  lines and unique spectral features of the companion. limited stellar  the host and choice, with only a small number of stellar lines to get a good fit of the host, and  This wavelength range is likely not the best choice for the proposed study. For example \citet{passegger_fundamental_2016} use 4 different wavelength regions with lines from different species to fit PHOENIX-ACES models to M-dwarf stars while other studies aiming to detect planetary companions choose wavelength regions which contain strong planetary absorption features such as the absorption of CO and H$_2$O near 2.3 $\mu$m \citep[e.g.[]{dekok_detection_2013, brogi_carbon_2014}.
Applying the binary fitting to a different wavelength region with lines more sensitive to stellar parameters for both stars and BDs, as well as using a larger wavelength range (i.e. provided by the cross-dispersion on CRIRES+), should improve the recovery results of the technique presented here. We note that if the wavelength range is increased by taking separate observations at different wavelengths, not covered by a single exposure, then changes in the RV of both components between the different wavelength observations will need to be accounted for.}
